FraCaS: 80 percent complete

### 2019-02-28 paper2018/paper.tex
compression

\begin{abstract}
 In this paper, we present a system for Natural Language Inference which uses a Haskell dynamic semantics  converter from abstract syntax trees to Coq types. The system makes use of the fine-grainedness of a dynamic semantics system with the powerfulness of a state-of-the-art proof assistant, like Coq. We evaluate the system on all sections of the FraCaS test suite, excluding section 6. This is the first system that does a complete run on the anaphora and ellipsis sections of the FraCaS and has the best accuracy overall when compared with previous systems. 
\end{abstract}
\section{Introduction}
Natural Language Inference (NLI) is the task of determining of whether
an NL hypothesis H follows from an NL premise(s) P. NLI has received a
lot of attention in the Computational Semantics literature and has
been approached using a variety of techniques, ranging from logical
approaches
\citep{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy_type_2017},
all the way to the recent Deep Learning (DL) models for NLI. The
latter approaches, following a general trend in NLP, have been
dominating NLI and a number of impressive results have been
produced \citep{kim:2018,radford:2018,liu:2019}.\footnote{These are
  the three systems with the best results on SNLI in increasing
  order at the time of writing.}  State-of-the-art DL systems achieve an accuracy of around
0.9 when tested on suitable datasets. However, the datasets that are
used are assuming a definition of inference that can be thought to be
`looser' or less precise compared to the definition assumed in
platforms based in logical approaches. For example, consider the following
 example  from the SNLI dataset, predominatly used to test DL
approaches:
%
\begin{lingex}
\item % An SNLI example \\
  \label{ex:snli}
\textbf{P}  A  man selling donuts to a customer during a world
exhibition event held in the city of Angeles. \\
 \textbf{H}  A woman drinks her coffee in a small cafe.\\
\textbf{Label: Contradiction} [SNLI]
% \item % An example from FraCaS\\
% \textbf{P1} A Scandinavian won the Nobel Prize.\\
% \textbf{P2}	Every Swede is  Scandinavian.\\
% \textbf{Q}  Did a Swede win the Nobel prize? \\
% \textbf{H} A Swede won the Nobel prize.\\
% \textbf{Label: Yes} [FraCaS 173]
\end{lingex}
%
In \ref{ex:snli}, a number of non-trivial
assumptions have to be made in order to arrive at a contradiction: a) the two
situations described have to be taken to refer to the same situation
in order to judge that the latter  contradicts the former, b)
the indefinite article in the premise has to be identified with the
indefinite article in the hypothesis. (Additionally considering that a
person cannot be a man selling donuts and a woman drinking coffee at
the same time.) While this can be part of the reasoning humans
perform, it is not the only possibility. More precise, logical
reasoning is also a possibility, and will render the above label as unknown. Furthermore, reasoning can get very fine-grained 
as the Contained Deletion ellipsis example \ref{ex:acd} below shows:

@@

\section{Background: GF, Coq, Monadic Dynamic Semantics}

@@

All the underlying systems (GF, Haskell, Coq) are based on lambda
calculi with types. We take advantage of typing, ensuring that each
translation preserve typing, locally:
\begin{enumerate}
\item Every GF syntactic category $C$ is mapped to a type noted $⟦C⟧$.
\item GF Functional types are mapped compositionally : $⟦A → B⟧ = ⟦A⟧ → ⟦B⟧$
\item Every GF syntactic construction function ($f : X$) is mapped to a function $⟦f⟧$ such that $⟦f⟧ : ⟦X⟧$.
\item GF function applications are mapped compositionally: $⟦t(u)⟧ = ⟦t⟧ (⟦u⟧)$.
\end{enumerate}
Because all systems embed the simply-typed lambda calculus, ensuring
type-preservation locally means that types are preserved globally.
Therefore, we are certain that every GF syntax tree can be mapped to
Haskell, and eventuall Coq, without error.

>>>>

\begin{abstract}
  We present a system for Natural Language Inference which uses a
  dynamic semantics converter from abstract syntax trees to Coq
  types. It combines the fine-grainedness of a dynamic semantics
  system with the powerfulness of a state-of-the-art proof assistant,
  like Coq. We evaluate the system on all sections of the FraCaS test
  suite, excluding section 6. This is the first system that does a
  complete run on the anaphora and ellipsis sections of the FraCaS. It
  has a better overall accuracy than any previous system.
\end{abstract}
\section{Introduction}
Natural Language Inference (NLI) is the task of determining of whether
an NL hypothesis H follows from an NL premise(s) P. NLI has received a
lot of attention in the Computational Semantics literature and has
been approached using a variety of techniques, ranging from logical
approaches
\citep{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy_type_2017},
all the way to the recent Deep Learning (DL) models for NLI. The
latter approaches, following a general trend in NLP, have been
dominating NLI and a number of impressive results have been
produced \citep{kim:2018,radford:2018,liu:2019}.\footnote{These are
  the three systems with the best results on SNLI in increasing
  order at the time of writing.}  State-of-the-art DL systems achieve an accuracy of around
0.9 when tested on suitable datasets. However, the datasets that are
used are assuming a definition of inference that can be thought to be
`looser' or less precise compared to the definition assumed in
platforms based in logical approaches. For example, consider the following
 example  from the SNLI dataset, predominatly used to test DL
approaches:
%
\begin{lingex}
\item % An SNLI example \\
  \label{ex:snli}
\textbf{P}  A  man selling donuts to a customer during a world
exhibition event held in the city of Angeles. \\
 \textbf{H}  A woman drinks her coffee in a small cafe.\\
\textbf{Label: Contradiction} [SNLI]
% \item % An example from FraCaS\\
% \textbf{P1} A Scandinavian won the Nobel Prize.\\
% \textbf{P2}	Every Swede is  Scandinavian.\\
% \textbf{Q}  Did a Swede win the Nobel prize? \\
% \textbf{H} A Swede won the Nobel prize.\\
% \textbf{Label: Yes} [FraCaS 173]
\end{lingex}
%
In \ref{ex:snli}, a number of non-trivial
assumptions have to be made in order to arrive at a contradiction: a) the two
situations described have to be taken to refer to the same situation
in order to judge that the latter  contradicts the former, b)
the indefinite article in the premise has to be identified with the
indefinite article in the hypothesis. (Additionally considering that a
person cannot be a man selling donuts and a woman drinking coffee at
the same time.) While this can be part of the reasoning humans
perform, it is not the only possibility. More precise, logical
reasoning is also a possibility, and will render the above label as unknown. Furthermore, reasoning can get very fine-grained 
as the Contained Deletion ellipsis example \ref{ex:acd} below shows:

@@

\section{Background}

@@

All the underlying systems (GF, Haskell, Coq) are based on lambda
calculi with types. We take advantage of typing, ensuring that each
translation preserve typing, locally:
\begin{enumerate}[noitemsep]
\item Every GF syntactic category $C$ is mapped to a type noted $⟦C⟧$.
\item GF Functional types are mapped compositionally : $⟦A → B⟧ = ⟦A⟧ → ⟦B⟧$
\item Every GF syntactic construction function ($f : X$) is mapped to a function $⟦f⟧$ such that $⟦f⟧ : ⟦X⟧$.
\item GF function applications are mapped compositionally: $⟦t(u)⟧ = ⟦t⟧ (⟦u⟧)$.
\end{enumerate}
Because all systems embed the simply-typed lambda calculus, ensuring
type-preservation locally means that types are preserved globally.
Therefore, we are certain that every GF syntax tree can be mapped to
Haskell, and eventually Coq, without error.
